---
title: "HW1"
author: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# HW1
### Q1. (4 points)
Recall that a Poisson (or NB) has the following relationship between the mean and covariates:

\begin{align}
  y_i & \sim Poisson(\mu_i)\\
  \log(\mu_i) & = X_i \beta
\end{align}

Assess the model fit between casual user bike rentals and centered temperature and determine if transformations of centered temperature would result in a better fit. Defend your choice.

```{r, message = F}
bikes <- read_csv("https://raw.githubusercontent.com/STAT506/GLM_Lectures/main/daily_bike.csv")
bikes <- bikes %>% mutate(temp_centered = temp - mean(temp))
```

\vfill

```{r, echo = F}
bikes %>% ggplot(aes(y = casual, x = temp)) + geom_point(alpha = .5) + theme_bw() +
  ggtitle("Casual User Bike Rentals vs Centered Temperature") +
  xlab('Centered Temperature') + ylab('daily rentals') +
  geom_smooth(formula = 'y~x', method = 'loess', se = F)
```

\newpage

### Q2. 

#### a. (4 points)

Write an R function or chunk of code to simulate data from a negative binomial regression model using a single covariate and a user specified value of $\phi$.

#### b. (4 points)

Use the following four values of $\phi:$ {.1, 1, 50, 1000} and simulate a dataset. Create a paneled figure that shows y and x for each scenario.

#### c. (4 points)
Use `stan_glm()` to fit Poisson models and Negative Binomial models for each of the four simulated datasets. Create a table or figure that contains the intercept and slope coefficient for each outcome. Then comment on the implications of your results.

#### c. (4 points)
Use `stan_glm()` to fit Poisson models and Negative Binomial models for each of the four simulated datasets. Create a table or figure that contains the intercept and slope coefficient for each outcome. Then comment on the implications of your results.

#### d. (5 points)

Use `posterior_predict()` and posterior predictive checks to further interrogate the model fit (using the Poisson models)